%Although a large number of applications produce time-varying vector fields, many limit subsequent analysis to single time slices due to constraints on data storage.
%%
%In recent years, reduced Lagrangian representations of time-varying vector fields have been researched as a potential approach to enable accurate post hoc analysis.
%%
%The utility of this technique, however, varies based on the nature of the vector field, and the configuration specifics that determine computation costs as well as storage requirements.
%%In recent years, reduced Lagrangian representations of time-varying vector fields have been considered to enable accurate post hoc analysis.
%%
%This paper contributes the investigation of Lagrangian representations computed in situ for two application domains: cosmology and seismology.
%%
%%These applications generate time-varying vector fields that vary in nature to those previously studied.
%%
%To investigate utility, we evaluate effectiveness and viability. 
%%
%To inform effectiveness, our study conducted a statistical analysis of efficacy across a range of spatiotemporal configurations as well as a qualitative evaluation. %comparison of the technique to the traditional Eulerian approach.
%%
%To inform viability, we considered representative HPC environments, integrated in situ infrastructure with the simulation codes, and performed Lagrangian in situ reduction using GPUs as well as CPUs.
%%
%We found that time-varying vector fields produced by the cosmology and seismology applications considered can be reduced by 200X via Lagrangian representations, while maintaining accurate reconstruction and requiring under 10\% of total execution time in 11 of 13 experiments.
%%In particular, we found Lagrangian representations for data generated by the Nyx cosmology simulation are sensitive to both spatial and temporal sampling, notably providing higher accuracy as temporal sparsity increases.
%%
%%For the SW4 seismology simulation, we found Lagrangian representations can accurately encode time-varying vector fields for seismic wave propagation and offer strong data reduction propositions.
%%
%%Additionally, we include results from a benchmarking study using an ECP mini-application that utilizes heterogenous compute resources.
%%
%%Overall, the in situ processing cost to compute Lagrangian representations was under 10\% of total execution time in 11 of 13 experiments.
%%
%
%\fix{HANK:}
Although many types of computational simulations produce time-varying vector fields, 
subsequent analysis is often limited to single time slices due to excessive costs.
%
Fortunately, a new approach using a Lagrangian representation can 
enable time-varying vector field analysis while mitigating these costs.
%
With this approach, a Lagrangian representation is calculated while the simulation code is running, and the result is explored after the simulation.
%
Importantly, 
 the effectiveness of this approach varies based on the nature of the vector field, 
requiring in-depth investigation for each application area.
%
With this study, we evaluate the effectiveness for previously unexplored cosmology and seismology
applications. %, which have previously been unexplored.
%
We do this by considering encumbrance (on the simulation to calculate the
Lagrangian representation) and also efficacy (of the reconstructed result).
%
To inform encumbrance, we 
integrated in situ infrastructure with two simulation codes, 
and evaluated on representative HPC environments,
performing Lagrangian in situ reduction using GPUs as well as CPUs.
%
To inform efficacy, our study conducted a statistical analysis across a range of spatiotemporal configurations as well as a qualitative evaluation.
%
In all, we demonstrate effectiveness for both cosmology and seismology --- time-varying vector fields from these domains can be reduced by 200X via Lagrangian representations, while maintaining accurate reconstruction and requiring under 10\% of total execution time in over 80\% of our experiments.
