Accurate exploratory analysis and visualization of time-varying vector fields is challenging.
%
On the one hand, it can be performed accurately if the entire spatiotemporal resolution is available.
%
However, storing all the data to disk for exploratory post hoc analysis is expensive.
%
On the other hand, if subsets of the data are stored, predicting uncertainty and variability of efficacy for analysis techniques post hoc is difficult.
%
In this context, Lagrangian representations computed using the full spatiotemporal resolution via in situ processing demonstrate the potential to enable accurate exploratory time-varying vector field analysis for reduced data storage costs.


%can enable exploratory time-varying vector field analysis.

For wider adoption and consideration of Lagrangian representations, an important step is characterization of effectiveness across a broad range of real-world applications.
%
In this paper, we investigated in situ reduction via Lagrangian representations for vector fields from Nyx cosmology and SW4 seismology simulations.
%
For the Nyx cosmology simulation, we found that Lagrangian representations are sensitive to both the spatial and temporal sampling rate.
%
Notably, providing higher reconstruction accuracy when basis trajectories are computed using a high spatial and low temporal resolution.
%
For the SW4 seismology simulation, we found Lagrangian representations are inherently suited to capture the transient seismic waves and offer high data reduction options for a small loss of accuracy.
%
For both simulations, the percentage of execution time spent on computing the Lagrangian representation in situ was under 10\% in most cases.
%
Overall, we believe the two computational science simulations considered and many others could benefit from Lagrangian representations to enable time-varying vector field exploration. 
